HEP Software Foundation Community White Paper Working Group -- Training, Staffing and Careers

### 2018-07-18 CWP/papers/HSF-CWP-2017-02_training/latex/cwp-wg-training-careers.tex
Missed middle initial (#99)
Add new authors to the Training paper

\author[1]{Dario Berzano,}
\author[2]{Riccardo Maria Bianchi,}
\author[3]{Peter Elmer,}
\author[1]{John Harvey,}
\author[4]{Roger Jones,}
\author[5]{Michel Jouvin,}
\author[6]{Daniel S. Katz,}
\author[7]{Sudhir Malik,}
\author[8]{Dario Menasce,}
\author[6]{Mark Neubauer,}
\author[9,a]{Albert Puig,}
\author[1]{Graeme Stewart,}
\author[10]{and Christopher Tunnell}

\affiliation[1]{CERN, Geneva, Switzerland}
\affiliation[2]{Department of Physics and Astronomy, University of Pittsburgh, Pittsburgh, PA, USA}
\affiliation[3]{Princeton University, Princeton, NJ, USA}
\affiliation[4]{Lancaster University, Lancaster, UK}
\affiliation[5]{LAL, Université Paris-Sud and CNRS/IN2P3, Orsay, France}
\affiliation[6]{University of Illinois Urbana-Champaign, Urbana, IL, USA}
\affiliation[7]{University of Puerto Rico, Mayaguez, PR, USA}
\affiliation[8]{INFN Sezione di Milano-Bicocca, Italy}
\affiliation[9]{Physik-Institut, Universität Zürich, Zürich, Switzerland}
\affiliation[10]{University of Chicago, Chicago, IL, USA}
\affiliation[a]{Supported by SNF under contract 168169.}

>>>>

\author[1]{Dario Berzano,}
\author[2]{Riccardo Maria Bianchi,}
\author[3]{Peter Elmer,}
\author[4]{Sergei V. Glayzer}
\author[1]{John Harvey,}
\author[5]{Roger Jones,}
\author[6]{Michel Jouvin,}
\author[7]{Daniel S. Katz,}
\author[8]{Sudhir Malik,}
\author[9]{Dario Menasce,}
\author[7]{Mark Neubauer,}
\author[10]{Fernanda Psihas}
\author[11,a]{Albert Puig,}
\author[1]{Graeme A. Stewart,}
\author[12]{Christopher Tunnell,}
\author[10]{Justin A. Vasel,}
\author[4]{and Sean-Jiun Wang}

\affiliation[1]{CERN, Geneva, Switzerland}
\affiliation[2]{Department of Physics and Astronomy, University of Pittsburgh, Pittsburgh, PA, USA}
\affiliation[3]{Princeton University, Princeton, NJ, USA}
\affiliation[4]{University of Florida, Gainesville, FL, USA}
\affiliation[5]{Lancaster University, Lancaster, UK}
\affiliation[6]{LAL, Université Paris-Sud and CNRS/IN2P3, Orsay, France}
\affiliation[7]{University of Illinois Urbana-Champaign, Urbana, IL, USA}
\affiliation[8]{University of Puerto Rico, Mayaguez, PR, USA}
\affiliation[9]{INFN Sezione di Milano-Bicocca, Italy}
\affiliation[10]{Department of Physics, Indiana University, Bloomington, IN,
USA}
\affiliation[11]{Physik-Institut, Universität Zürich, Zürich, Switzerland}
\affiliation[12]{University of Chicago, Chicago, IL, USA}
\affiliation[a]{Supported by SNF under contract 168169.}
